R Notebook

### 2024-07-05 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Added script to visualise combined relative and absolute intervention together. Also added some things to gitignore

---
title: "Scottish Child Poverty Briefing Plots"
output:
  pdf_document:
    toc: true
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

WS5 (Dynamic Microsimulation): What are the impacts on mental health of meeting the targets?
·        Across the population? 
·        Population by income quintile (looking at absolute/relative inequalities)?
·        For families only? By income quintile (looking at absolute/relative inequalities)?
·        For families that meet criteria of 0/1/2+ of the priority family groups?
·        Differential impacts of UK package of policies only, and then UK package with SG policies?

@@

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/psub/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/default_US/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

```{r "Data", include=FALSE}
scen.list.rel <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
scen.rel <- 'ChildPovertyReductionRELATIVE_2'
scen.list.abs <- c('baseline', 'ChildPovertyReductionABSOLUTE')
scen.abs <- 'ChildPovertyReductionABSOLUTE'
# scen.list.rel <- c('baseline', 'ChildPovertyReductionRELATIVE_psub')
# scen.rel <- 'ChildPovertyReductionRELATIVE_psub'
# scen.list.abs <- c('baseline', 'ChildPovertyReductionABSOLUTE_psub')
# scen.abs <- 'ChildPovertyReductionABSOLUTE_psub'
```

# MCS Change to QALY Example

We use an equation derived from table 4 (below) in [this paper by Lawrence and Fleishman](https://pubmed.ncbi.nlm.nih.gov/15090102/) to calculate QALYs from SF-12 Mental Component Score (MCS) and Physical Component Score (PCS).

#![L&F Table 4](L&F_table4.png)

```{r}
# formula to find the utility score from mean MCS and PCS scores of a population
utility_score <- function(pcs, mcs) {
  utility_score <- 
    1.6984 + 
    (pcs * 0.07927) +
    (mcs * 0.02859) +
    ((pcs * mcs) * -0.000126) +
    ((pcs * pcs) * -0.00141) +
    ((mcs * mcs) * -0.00014) +
    ((pcs * pcs * pcs) * 0.0000107)
  return(utility_score)
}

# Calculate utility score for hypothetical baseline (MCS & PCS == 45.0)
initial_conditions <- utility_score(pcs = 45.0,
                                    mcs = 45.0)
# Calculate utility score for 0.1 improvement in MCS (MCS now == 45.1)
intervention <- utility_score(pcs = 45.0,
                              mcs = 45.1)

print("Utility score for hypothetical baseline (assuming mean MCS and PCS both equal 45.0):")
print(initial_conditions)
print("Utility score for population given a 0.1 mean improvement in MCS:")
print(intervention)

print("Gain in utility score per person:")
gain <- intervention - initial_conditions
print(gain)

print("Gain in utiliy for the total Scotland population (assuming 5.5m). This is equivalent to QALYs gained:")
print(gain * 5500000)
```

This rough calculation shows that a 0.1 absolute change in mean SF_12 across the Scottish population would equal over 5000 additional QALYs in a single year. These improvements can also accumulate over time. If we were able to achieve a 0.1 improvement in mean MCS for Scotland in year 1, and maintain this 0.1 improvement for 10 years, the resulting improvement in QALYs would be 56,000+.

NOTE: This calculation assumes that PCS is unchanged when MCS can vary. This is not realistic, but the calculation is still useful to provide context for the results to follow.

# SAMPLE UNCERTAINTY

When running MINOS with a synthetic population, due to the size of the synthetic populations and the demands of the model, we have to take a reduced sample as our starting population. For the Scotland synthetic runs we take a 10% sample, which reduces the population size from roughly 5.5m to 550,000.

We therefore have to also account for the uncertainty in model outputs that comes from this reduced sample. As a somewhat temporary fix for this, we have done the following:

- Generate 10 different 10% samples from our synthetic population
  - Generate a replenishing population from each of these samples
- Use each distinct 10% sample for 10 runs each, totalling 100 runs
- Plot the local mean from each 10 run block, and the global mean from all 100 runs

```{r}
synthpop_uncertainty(summary_group = 'whole_pop',
                     scen = 'baseline',
                     var = 'hh_income')

synthpop_uncertainty(summary_group = 'whole_pop',
                     scen = 'baseline',
                     var = 'SF_12')
```

# RELATIVE POVERTY INTERVENTION

Reducing the proportion of children in poverty to 10% or lower by 2030.

@@

```{r}
SF12_change_simple(summary_group = 'whole_pop',
                   scen.list = scen.list.rel)

SF12_change_ind_trajectories(summary_group = 'whole_pop',
                             scen.list <- scen.list.rel)

mental_illness_risk_counts(summary_group = 'men_illness_risk',
                           scen.list = scen.list.rel)
```

@@

```{r}
# SF12_change_income_quint(summary_group = 'whole_pop',
#                                     scen.list = scen.list.rel)
SF12_change_income_quint2(summary_group = 'whole_pop',
                                    scen = scen.rel)
```

@@

```{r}
inequality_plots(summary_group = 'whole_pop',
                 scen = scen.rel)
```

@@

```{r}
SF12_change_simple(summary_group = 'families',
                       scen.list = scen.list.rel)

SF12_change_ind_trajectories(summary_group = 'families',
                             scen.list <- scen.list.rel)

mental_illness_risk_counts(summary_group = 'men_illness_risk_families',
                           scen.list = scen.list.rel)
```

@@

```{r}
# SF12_change_income_quint(summary_group = 'families',
#                                     scen.list = scen.list.rel)
SF12_change_income_quint2(summary_group = 'families',
                                    scen = scen.rel)
```

@@

```{r}
inequality_plots(summary_group = 'families',
                 scen = scen.rel)
```

@@

```{r}
SF12_change_simple(summary_group = 'priority_any',
                       scen.list = scen.list.rel)
```

@@

```{r}
SF12_change_num_priority_groups(scen.list.rel)
```

@@

SF12_change_treated(scen = scen.rel)
```

## Differential Impacts of UK vs SG

What are the impacts on mental health of meeting the targets?

- Differential impacts of UK package of policies only, and then UK package with SG policies?

# ABSOLUTE POVERTY INTERVENTION

Reducing the proportion of children in poverty to 10% or lower by 2030.

```{r}
SF12_change_simple(summary_group = 'whole_pop',
                       scen.list = scen.list.abs)

SF12_change_ind_trajectories(summary_group = 'whole_pop',
                             scen.list <- scen.list.abs)

mental_illness_risk_counts(summary_group = 'men_illness_risk',
                           scen.list = scen.list.abs)
```

```{r}
# SF12_change_income_quint(summary_group = 'whole_pop',
#                                     scen.list = scen.list.abs)
SF12_change_income_quint2(summary_group = 'whole_pop',
                                    scen = scen.abs)
```

```{r}
inequality_plots(summary_group = 'whole_pop',
                 scen = scen.abs)
```

```{r}
SF12_change_simple(summary_group = 'families',
                       scen.list = scen.list.abs)

SF12_change_ind_trajectories(summary_group = 'families',
                             scen.list <- scen.list.abs)

mental_illness_risk_counts(summary_group = 'men_illness_risk_families',
                           scen.list = scen.list.abs)
```

```{r}
# SF12_change_income_quint(summary_group = 'families',
#                                     scen.list = scen.list.abs)
SF12_change_income_quint2(summary_group = 'families',
                                    scen = scen.abs)
```

```{r}
inequality_plots(summary_group = 'families',
                 scen = scen.abs)
```

```{r}
SF12_change_simple(summary_group = 'priority_any',
                                    scen.list = scen.list.abs)
```

```{r}
SF12_change_num_priority_groups(scen.list.abs)
```

```{r}
# SF12_change_simple(summary_group = 'treated_absolute',
#                    scen.list = scen.list.abs)

SF12_change_treated(scen = scen.abs)
```

## Differential Impacts of UK vs SG

What are the impacts on mental health of meeting the targets?

- Differential impacts of UK package of policies only, and then UK package with SG policies?

>>>>

---
title: "R Notebook"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

@@

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

```{r "Data", include=FALSE}
scen.list <- c('baseline', 'ChildPovertyReduction')
scen <- 'ChildPovertyReduction'
```

# COMBINED RELATIVE AND ABSOLUTE REDUCTION INTERVENTION

@@

```{r}
SF12_change_simple(summary_group = 'whole_pop',
                   scen.list = scen.list)

SF12_change_ind_trajectories(summary_group = 'whole_pop',
                             scen.list <- scen.list)

mental_illness_risk_counts(summary_group = 'men_illness_risk',
                           scen.list = scen.list)
```

@@

```{r}
# SF12_change_income_quint(summary_group = 'whole_pop',
#                                     scen.list = scen.list.rel)
SF12_change_income_quint2(summary_group = 'whole_pop',
                                    scen = scen)
```

@@

```{r}
inequality_plots(summary_group = 'whole_pop',
                 scen = scen)
```

@@

```{r}
SF12_change_simple(summary_group = 'families',
                       scen.list = scen.list)

SF12_change_ind_trajectories(summary_group = 'families',
                             scen.list <- scen.list)

mental_illness_risk_counts(summary_group = 'men_illness_risk_families',
                           scen.list = scen.list)
```

@@

```{r}
# SF12_change_income_quint(summary_group = 'families',
#                                     scen.list = scen.list.rel)
SF12_change_income_quint2(summary_group = 'families',
                                    scen = scen)
```

@@

```{r}
inequality_plots(summary_group = 'families',
                 scen = scen)
```

@@

```{r}
SF12_change_simple(summary_group = 'priority_any',
                       scen.list = scen.list)
```

@@

```{r}
SF12_change_num_priority_groups(scen.list)
```

@@

SF12_change_treated(scen = scen)
```
